INTELLIGENT SYSTEMS

### 2021-04-17 slides/slides_paper8.tex
finish slides of paper8

\begin{frame}{METHODS - \emph{Template-Searching-Background Loss} (TSB)}

\end{frame}

>>>>

\begin{frame}{METHODS - \emph{Template-Searching-Background Loss} (TSB)}
    The use of the Template-Searching-Background (TSB), allows to use the 
    background patches to train the model. This method helps to minimize 
    the relative distance $d(\cdot)$ (\ref{distanceFunc}) which translated into other words means 
    bringing the target template closer to the $X_i^+$ samples and at the same 
    time moving the background distractors $B_i$ away from the positive 
    sample.
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{block}{RELATIVE DISTANCE}
                \begin{equation}\label{distanceFunc}
                    d_i=\sum^M_{j=1} D(T, X_i) - D(X_i, B_{i-1,j})
                \end{equation}
            \end{block}  
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.47\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width =\linewidth]{images/paper8/TSB.png}
                \centering
            \end{figure}
        \end{minipage}
    \end{minipage}
\end{frame}

\begin{frame}{METHODS - Tracking With Updating}
    To evaluate the correspondence of an $X_i^+$ patch, a \emph{Trust Score s} is calculated. The score $s$ will be compared with two thresholds $\sigma_1$ and $\sigma_2$.
    If $s\leq\sigma_1$ then a new positive patch $X{'}_i^+$, and consequently a new score $s'$, will be recalculated which will be replaced with the previous patch $X_i^+$ when $s'\geq\sigma_1$.
    If $s\geq\sigma_2$ then update the target template $T$ with $X_i^+$.
    \begin{equation}\label{distanceFunc}
        X_i = \argmin_{X_{i,k} \in S_i}d(T,X_{i,k}, \{B_{i-1,j}\}^M_{j=1})
    \end{equation}
    \begin{equation}\label{newX}
        X'_i = \argmax_{X_{i,k} \in S_i}m(T,X_{i,k})
    \end{equation}
\end{frame}

\begin{frame}{EXPERIMENTS}
    The experiments were conducted on four different types of datasets: 
    OTB-2013, OTB-100, VOT-2015 and VOT-2016. The metrics used to 
    evaluate the performance of all existing methods, including the one 
    proposed, are accuracy, Area-Under-the-Curve (AUC), 
    Expected-Average-Overlap (EAO) and robustness.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/metrics.png}
        \centering
    \end{figure}
\end{frame}

\begin{frame}{EXPERIMENTS - AUC score on distractors}
    Target tracking can be onerous when there are elements such as 
    distractors in the scene. These lead most trackers to fail. The 
    re-verification and re-detecting operations were essential to reduce this 
    problem. In the table, the values in blue are the highest and are obtained 
    from the best method, while those in red are placed in second position.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/AUC.png}
        \centering
    \end{figure}
\end{frame}

\begin{frame}{CONCLUSION}
    The proposed framework, from the results obtained in the benchmarks, seems 
    to be the best. The achievement of these results were possible thanks to the 
    integration of a verification and detecting method. The use of the TSB 
    method was fundamental, which, by reducing the relative distance between 
    the various patches, allowed for good model learning.
\end{frame}
